%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Sahil Jagtap}\\ {Fairfax, Virginia}\\ \vspace{1pt}
    \small +1 703-826-3790 $|$ \href{mailto:sjagtap2@gmu.edu}{\underline{sjagtap2@gmu.edu}} $|$ 
    \href{https://linkedin.com/in/sahiljagtap08}{\underline{linkedin.com/in/sahiljagtap08}} $|$
    \href{https://github.com/sahiljagtap08}{\underline{github.com/sahiljagtap08}}
    $|$
    \href{https://sahiljagtap.com}{\underline{sahiljagtap.com}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {George Mason University - Honors}{Fairfax, VA}
      {Bachelor of Science in Computer Science}{Aug. 2022 -- May 2026}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Microsoft $|$ NASA}{May 2023 ‑- June 2023}
      {Microsoft Azure Space ‑ 5 Weeks Internship Program}{Remote \& Arlington, VA}
      \resumeItemListStart
       \resumeItem {Set up a planetary computer environment to facilitate efficient data processing and analysis.}
       \resumeItem {Created a high-level paper-based architecture of the application, outlining the key components.}
        \resumeItem {Ingested Sentinel-1 data from the planetary computer platform to acquire relevant satellite imagery.}
        \resumeItem {Reviewed existing algorithms and techniques to inform the design of the detection model.}
        \resumeItem { Selected features and metrics, trained the model using Python and Jupyter Notebook.}
        \resumeItem {Trained the model using the prepared data, fine-tuning its parameters for optimal performance.}
        \resumeItem {Deployed the planetary computer application, ensuring its scalability and efficient utilization of resources.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Information Technology Intern}{May. 2023 -- Aug. 2023}
      {Precise Systems Inc. - Summer Internship 2023}{Manassas, VA}
      \resumeItemListStart
         \resumeItem {Collaborated with the IT team at Precise Systems to support and enhance the company's website, playing a key role in improving its functionality and user experience.}
        \resumeItem {Assisted in the development and maintenance of the company website, utilizing web technologies such as HTML, CSS, and JavaScript to implement new features and resolve issues.}
        \resumeItem {Conducted thorough testing and quality assurance to identify and fix bugs or errors in the website.}
        \resumeItem {Played a vital role in designing and deploying a scalable and reliable database infrastructure for the project.}
    \resumeItemListEnd

    \resumeSubheading
      {President}{April 2023 -- Present}
      {DSCS-GMU, Chapter at the NSDC - Columbia University}{Fairfax, VA}
      \resumeItemListStart
        \resumeItem {Established strong collaborations with academic departments, industry professionals, and external organizations including the National Student Data Corps at \emph{Columbia University}, facilitating internship opportunities, research partnerships, and networking avenues for society members.}
        \resumeItem {Developed and executed a comprehensive strategy to drive awareness and engagement, resulting in a significant increase in membership and active participation within the \emph{Data Science and Computation Society.} }
        \resumeItem {Organized and curated a series of impactful events, including data science workshops, seminars, and guest speaker sessions, providing valuable learning opportunities and industry insights to members.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{HackMIT - 2nd Place (TerraAPI Track Prize Winner} $|$ \emph{Next.js, Firebase, TerraAPI, GPT-4, Git}}{Sep. 2022}
          \resumeItemListStart
       \resumeItem {Utilized Next.js for the frontend development, creating an interactive and engaging user interface.}
    \resumeItem {Implemented Firebase for the backend, ensuring secure and efficient data storage and retrieval.}
    \resumeItem {Integrated TerraAPI to access and transform daily activity and health data into a virtual character.}
    \resumeItem {Leveraged GPT-4 and DALL·E 2 to provide a dynamic and personalized character experience.}
    \resumeItem {Incorporated mathematical algorithms to calculate and reflect real-life health and energy levels in the character.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Metro-Rail-App} $|$ \emph{C++, Graph, Heap, Dijkstra's Algorithm, BFS, DFS.}}{July 2023}
          \resumeItemListStart
           \resumeItem{Developed a C++ program to assist commuters in the Metro system by providing shortest routes.}
\resumeItem{Implemented the project using Graph and Heap data structures, with nodes representing metro stations and edges representing distances and costs between stations.}
\resumeItem{Utilized Dijkstra algorithms, BFS, and DFS to determine the shortest path between source and destination.}
\resumeItem{Demonstrated proficiency in C++ programming and data structures to solve real-world transportation problems.}

          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Java, Python, SQL(MySQL, Postgres), JavaScript, HTML/CSS} \\
     \textbf{Frameworks \& Libraries}{: Express.js, React, Node.js, Flask, JUnit, TailwindCSS, Pandas, NumPy, Matplotlib} \\
     \textbf{Developer Tools}{: Git, GitHub, Linux, Jupyter, Docker, VS Code, PyCharm, IntelliJ} \\
      \textbf{Computer Science (Core)}{: OOPs, Data Structures, Algorithms, Mathematics, OS, DBMS, Computer Networking.}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
